### 2023-02-02 definitions.tex
details

@@

\begin{remark} 
$k$-resilienc $\leq$ bounded Resilience $\leq$ Resilience.  \textcolor{red}{AVERIFIER !!}
\end{remark}

\alain{examiner les cas I,J un élement, cloture, tout, clos par le bas et par le haut,... ...}

\begin{proposition}\label{reductions}
coverability are $t$-liveness reduceable to resilience.
%	home state and reachability
\end{proposition}

@@

\alain{dire juste que SAFE = upward closed et BAD = downward closed.
envisager les 3 autres cas. souvent BAD = upward closed (par ex l'exclusion mutuelle).
4 resilience problem (U,D), (U,U), (D,U), (D,D)}
% \textcolor{red}{In the Özkan paper the input include a basis of $\uparrow post^*(s)$. Not $100$\% sure it is necessary, think we can try to do without this assumption in the input.}

@@

The author in \cite{DBLP:conf/gg/Ozkan22}
%\"Ozkan
 goes on to prove that for finite-branching WSTS with strong monotonicity, a basis of $\uparrow \post^*(s)$ is computable for every given state $s$ iff the downward-closed problem is decidable, i.e. given a state $s$ of a WSTS
% in the regarded class 
with strong monotonicity 
and a decidable downward-closed set $J$, it can be decided whether $\exists s' \in J ~ s \to^* s'$ (Proposition~1 in \cite{DBLP:conf/gg/Ozkan22}). 
The characterization is used to show that Petri nets are $\post^*$-effective. It is well-known that Petri nets constitute WSTS with strong monotonicity (Thm.~6.1 in \cite{DBLP:journals/tcs/FinkelS01}).
However, the hypothesis that $\uparrow \post^*$ is computable cannot be tested in the general WSTS framework.

@@

\begin{proof}
Let us show that Reset VASS and LCS don't enjoy the property that $\uparrow \post^*$ is computable.
Suppose that one are able to compute a finite basis of $\uparrow post^*$ for Reset VASS. Then, one would be able to decide whether $0$ is reachable in counter $i$ by examining if there is some vector $v$ in the basis such that $v(i)=0$. But reachability of $0$ in a counter $i$ is undecidable for Reset VASS. 
% sont WSTS with strong compatibility. et l'accessibilité est undecidable.
$\uparrow post^*$ n'est pas calculable pour les LCS non plus car $\uparrow post^*= \uparrow \downarrow post^*$ n'est pas calculable ???
\textcolor{red}{à relire par Mathieu}
\end{proof}

il existe des modèles où on peut calculer $\uparrow post^*$: inserted channel systems: on sait calculer $post^*$ qui est rationnel donc on sait calculer $\uparrow post^*$.

>>>>

\alain{dire juste que SAFE = upward closed et BAD = downward closed.
envisager les 3 autres cas. souvent BAD = upward closed (par ex l'exclusion mutuelle).
4 resilience problem (U,D), (U,U), (D,U), (D,D)}

@@

\begin{remark} 
$k$-resilienc $\leq$ bounded Resilience 
%	$\leq$ Resilience.  
\textcolor{red}{oui si strong monootony, non ? sinon}
\end{remark}

\begin{proposition}\label{reductions}
coverability and $t$-liveness are reduceable to resilience.
%	home state and reachability
\end{proposition}

@@

% \textcolor{red}{In the Özkan paper the input include a basis of $\uparrow post^*(s)$. Not $100$\% sure it is necessary, think we can try to do without this assumption in the input.}

@@

The author in \cite{DBLP:conf/gg/Ozkan22}
%\"Ozkan
\begin{proposition}
goes on to prove that for finite-branching WSTS with strong monotonicity, a basis of $\uparrow \post^*(s)$ is computable for every given state $s$ iff the downward-closed problem is decidable, i.e. given a state $s$ of a WSTS
% in the regarded class 
with strong monotonicity 
and a decidable downward-closed set $J$, it can be decided whether $\exists s' \in J ~ s \to^* s'$ (Proposition~1 in \cite{DBLP:conf/gg/Ozkan22}). 
\end{proposition}

The characterization is used to show that Petri nets are $\post^*$-effective. It is well-known that Petri nets constitute WSTS with strong monotonicity (Thm.~6.1 in \cite{DBLP:journals/tcs/FinkelS01}).
However, the hypothesis that $\uparrow \post^*$ is computable cannot be tested in the general WSTS framework.

@@

\begin{proof}
Let us show that Reset VASS don't enjoy the property that $\uparrow \post^*$ is computable.
Suppose that one are able to compute a finite basis of $\uparrow post^*$ for Reset VASS. Then, one would be able to decide whether $0$ is reachable in counter $i$ by examining if there is some vector $v$ in the basis such that $v(i)=0$. But reachability of $0$ in a counter $i$ is undecidable for Reset VASS. 
% sont WSTS with strong compatibility. et l'accessibilité est undecidable.
%	$\uparrow post^*$ n'est pas calculable pour les LCS non plus car $\uparrow post^*= \uparrow \downarrow post^*$ n'est pas calculable ???
\textcolor{red}{à relire par Mathieu}
\end{proof}

%il existe des modèles où on peut calculer $\uparrow post^*$: inserted channel systems: on sait calculer $post^*$ qui est rationnel donc on sait calculer $\uparrow post^*$.
